surfing

### 2021-05-12 inst/surfing.Rmd
consistentify: put year in filename

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
QS <- rownames(surfing_table)[c(23:33,35:36)]
QS
```

```{r}
o <- strsplit(readLines("wct.txt")," ")
jj <- unlist(lapply(o,paste,collapse=" "))
head(jj)
tail(jj)
```

>>>>

```{r}
surfing_table <- read.table("wct_table2019.txt",header=TRUE)
options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
QS <- rownames(surfing_table)[c(23:33,35:36)]
QS
```

```{r}
o <- strsplit(readLines("wct2019.txt")," ")
jj <- unlist(lapply(o,paste,collapse=" "))
head(jj)
tail(jj)
```
